The role of seed-dispersing animal cognition in shaping plant distributions

### 2023-07-31 Text/Article_ModelSeedDispersal.Rmd
Update before submission

---
title: "The role of seed-dispersing animals in shaping plant distributions"
# "Animal cognition as a cause and consequence of resource distribution heterogeneity"
# "Eco-evolutionary feedback loops between animal cognition, movement and resource distribution"
# The role of animal cognition in shaping resource distribution via zoochory
# date: "`r format(Sys.time(), '%B %d, %Y')`"

>>>>

---
title: "The role of seed-dispersing animal cognition in shaping plant distributions"
# "Animal cognition as a cause and consequence of resource distribution heterogeneity"
# "Eco-evolutionary feedback loops between animal cognition, movement and resource distribution"
# The role of animal cognition in shaping resource distribution via zoochory
# date: "`r format(Sys.time(), '%B %d, %Y')`"

### 2023-07-31 Text/coverLetter.Rmd
Update before submission

```{r}
journal <- "Peer Community In Ecology"
editor <- "Recommenders of PCI"
title <- "The role of seed-dispersing animals in shaping plant distributions"
listOfAuthors <- paste("Benjamin Robira", collapse = ", ")
```

>>>>

```{r}
journal <- "Peer Community In Ecology"
editor <- "Recommenders of PCI"
title <- "The role of seed-dispersing animal cognition in shaping plant distributions"
listOfAuthors <- paste("Benjamin Robira", collapse = ", ")
```
